Process Genotypes For Ancestry Analysis

### 2019-09-20 code/Ancestry_PCA.Rmd
Update CacheStatus

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
#PATH=$PATH:TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done
```
```{bash FOO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

@@

### Finalize the MSBB LD SNP-Set Derived from WGS
```{bash FinalizeMSBB }
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

## Process MAYO Genotyping Data
```{bash MAYO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
```{bash CheckMayo}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

## Process ROSMAP Genotyping Data
```{bash DosageToHardCalls}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

##Merge the Genotype Sets and Preform PCA
```{bash MergeAndCall}

@@

##Plot PCA
```{r PlotPCA}

@@

## Cluster Based on Ancestry
```{bash CLustPrep}
plink --bfile Final_Merge --threads 32 --geno 0.0000001 --recode12 --compound-genotypes --out AllSnps4GemClust
#777864

>>>>

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, cache = FALSE, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
#PATH=$PATH:TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done

@@

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, cache = FALSE, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

@@

### Finalize the MSBB LD SNP-Set Derived from WGS
```{bash FinalizeMSBB, cache = FALSE  }
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

## Process MAYO Genotyping Data
```{bash MAYO, cache = FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
```{bash CheckMayo, cache = FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

## Process ROSMAP Genotyping Data
```{bash DosageToHardCalls, cache = FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

##Merge the Genotype Sets and Preform PCA
```{bash MergeAndCall, cache = FALSE}

@@

##Plot PCA
```{r PlotPCA, cache = FALSE}

@@

## Cluster Based on Ancestry
```{bash CLustPrep, cache = FALSE}
plink --bfile Final_Merge --threads 32 --geno 0.0000001 --recode12 --compound-genotypes --out AllSnps4GemClust
#777864
